---
title: "plotly"
output: 
  html_document:
     toc: true
     toc_flat: true
editor_options: 
  chunk_output_type: console
---
## Today we are making interactive plots with plotly

Mkaing examples using the NYC airbnb dataset.


```{r setup, include=FALSE}
library(flexdashboard)
```

```{r}
library(tidyverse)
library(p8105.datasets)
library(plotly)
```


Doing some data cleaning: 

```{r}

data(nyc_airbnb)

nyc_airbnb = 
  nyc_airbnb |> 
  mutate(rating = review_scores_location / 2) |> #five start scale
  select(
    neighbourhood_group, neighbourhood, rating, price, room_type, lat, long) |>
  filter(
    !is.na(rating), 
    neighbourhood_group == "Manhattan",
    room_type == "Entire home/apt",
    price %in% 100:500) #the in is between 
```

## Plotly Scatterplot 

```{r}
nyc_airbnb |>
  mutate(text_label = str_c("Price: $", price, "\nRating: ", rating, "\nNeighborhood: ", neighbourhood)) |> #this is the tooltip text that appears when you hover
  plot_ly(
    x = ~lat, y = ~long, 
    type = "scatter", 
    mode = "markers",
    color = ~price, 
    text = ~text_label, alpha = 0.5) #aesthetic markings of the plot
```

##Plotly Boxplot

```{r}
nyc_airbnb |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |> #reordering the variable by the price
  plot_ly(y = ~price, color = ~neighbourhood, type = "box", colors = "viridis")
```


## Plotly Barchart 
```{r }

nyc_airbnb |> 
  count(neighbourhood) |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) |> 
  plot_ly(x = ~neighbourhood, y = ~n, color = ~neighbourhood, type = "bar", colors = "viridis")
```

This lists the neighborhoods on the side and allows for more interaction. Double click to get the specific neighborhood. 

Now we do a bar plot 
```{r}

nyc_airbnb|>
   count(neighbourhood)|>
   mutate(neighbourhood=fct_reorder(neighbourhood, n))|>
   plot_ly(
      x= ~neighbourhood, y= ~n,
      type = "bar"
   )
```

## ggplotly
```{r}
scatter_ggplot = 
  nyc_airbnb |>
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point(alpha = 0.25) +
  coord_cartesian()

ggplotly(scatter_ggplot)
```


```{r}
box_ggplot = 
  nyc_airbnb |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |> 
  ggplot(aes(x = neighbourhood, y = price, fill = neighbourhood)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

ggplotly(box_ggplot)
```



## flexdashboard 

change the name and ouotput of the rmd. 


## flexdashboard on website 

using this command to knit in the dash

rmarkdown::render("dashboard_template.Rmd", output_format = "flexdashboard::flex_dashboard")


















